Climatic warming strengthens a positive feedback between alpine shrubs and fire

### 2016-03-08 manuscript/manuscript.Rnw
More updates

In total we built 11 hierarchical models to examine factors influencing tussock grass post-fire recovery and shrub seedling establishment, growth and mortality. For each model (Supplementary Methods) we used Bayesian inference and fitted models in R \Sexpr{paste(version$major, version$minor, sep='.')} using package Rstan \Sexpr{packageVersion("rstan")}. Data and source code for reproducing analysis and figures is available at: \url{https://github.com/jscamac/Alpine_Shrub_Experiment}.
\end{methods}

@@

\begin{figure}
\begin{minipage}{\textwidth}
\includegraphics{figures/fig2.pdf}
\caption{\textbf{Mean \textit{Grevillea australis} seedling density with burning, fire severity (minimum twig diameter), adult density, altitude and Topographic Wetness Index (TWI) gradients.} Centered and standardized model coefficients (on the log scale) (\textbf{a}) and effects of burning (\textbf{b}), fire severity  (\textbf{c}), altitude (\textbf{d}), topographic wetness (\textbf{e}) \& adult density (\textbf{f}), in areas burnt by the 2003 fires. All errors bars are 95\% Bayesian Credible Intervals.}
\label{fig2}
\end{minipage}
\end{figure}

>>>>

In total we built 11 hierarchical models to examine factors influencing tussock grass post-fire recovery and shrub seedling establishment, growth and mortality. For each model (Supplementary Methods) we used Bayesian inference and fitted models in R \Sexpr{paste(version$major, version$minor, sep='.')} using package Rstan \Sexpr{packageVersion("rstan")}. Data and source code for reproducing analysis and figures is available at: \url{https://github.com/jscamac/Alpine_Shrub_Experiment}. Additional information of experimental design and analysis can be found in Supplementary methods.
\end{methods}

@@

\begin{figure}
\begin{minipage}{\textwidth}
\includegraphics{figures/fig2.pdf}
\caption{\textbf{Mean \textit{Grevillea australis} seedling density along burning, fire severity (minimum twig diameter), adult density, altitude and Topographic Wetness Index (TWI) gradients.} Centered and standardized model coefficients (on the log scale) (\textbf{a}) and effects of burning (\textbf{b}), fire severity  (\textbf{c}), altitude (\textbf{d}), topographic wetness (\textbf{e}) \& adult density (\textbf{f}), in areas burnt by the 2003 fires. All errors bars are 95\% Bayesian Credible Intervals. Phi = overdispersion parameter for negative binomial distribution.}
\label{fig2}
\end{minipage}
\end{figure}
